Paper_analyses

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
plotting clusters vs ratings

clusplot(clust_dataset,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')

clustering_agg$y_kmeans<- y_kmeans

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

@@

@@

summary(pca_res)
```

@@

clusplot(clust_dataset,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')

>>>>

?clusplot
clusplot(clust_dataset,
         y_kmeans,
         lines = 2,
         shade = TRUE,
         color = TRUE,
         labels = 1,
         plotchar = FALSE,
         span = TRUE
         # label = 
         # main = paste('Clusters of customers'),
         # xlab = 'Annual Income',
         # ylab = 'Spending Score'
         )

a few visualisations
```{r}
clustering_agg$y_kmeans<- y_kmeans

@@

require(ggplot2)
# data("iris")

@@

clustering_agg$cluster_interpreted<- ifelse(clustering_agg$y_kmeans == 1, "mixed",
                                            ifelse(clustering_agg$y_kmeans == 2, "highlyarousing_aitated", "calmish"))
summary(pca_res)

# tsne plot
install.packages("tsne")
library(tsne)

?tsne

# install.packages("Rtsne")
require(Rtsne)
# install.packages("M3C")
# library(M3C)
tsne(clustering_agg[,c(20,24,25)])

# cluster vs ground arousal means
library(tidyverse)
clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
  # geom_point()+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()

clustering_agg %>%
  ggplot(aes(cluster_interpreted, ArousalMean))+
  # geom_point()+
  stat_summary(geom = 'pointrange')+
    ggpubr::stat_compare_means()

# cluster vs valence ground

# Visualize: Specify the comparisons you want
my_comparisons <- list( c("1", "2"), c("1", "3"), c("2", "3") )
my_comparisons <- list( c("mixed", "highlyarousing_aitated"), c("mixed", "calmish"), c("highlyarousing_aitated", "calmish") )
clustering_agg$cluster_interpreted
library(ggpubr)
ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ArousalMean",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)     # Add global p-value

clustering_agg %>%
  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg%>%
  ggplot(aes(cluster_interpreted, ValenceMean))+
  # geom_point()+
  stat_summary(geom = 'pointrange')+
    ggpubr::stat_compare_means()

ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ValenceMean",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

# based ins ample
clustering_agg %>%
  ggplot(aes(as.factor(y_kmeans), valence))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg %>%
  ggplot(aes(cluster_interpreted, valence))+
  # geom_point()+
  stat_summary(geom = 'pointrange')+
    ggpubr::stat_compare_means()

clustering_agg%>%
  ggplot(aes(cluster_interpreted, arousal))+
  # geom_point()+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()

cluster_stim<- select(clustering_agg, c(stimIAPS2,y_kmeans, cluster_interpreted, stimDescription))

# plot(test)
```

@@

?clusplot
clusplot(clust_dataset,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE
         # main = paste('Clusters of customers'),
         # xlab = 'Annual Income',
         # ylab = 'Spending Score'
         )
